### 2022-05-31 main/chapter_2ljets.tex
add files for figures: high design and disco significance

@@

>>>>

\TODO{}
\begin{verbatim}
2ljets_region_design_hist1d_mll_SRHigh.png
2ljets_region_design_hist1d_nbtag_SRHigh.png
\end{verbatim}

@@

\TODO{}
\begin{verbatim}
2ljets_disco_High_C1N2_WZ_500p0_200p0_2L2J.png
2ljets_disco_High_C1N2_WZ_600_0_2L2J.png
2ljets_disco_Int_C1N2_WZ_250p0_100p0_2L2J.png
2ljets_disco_Int_C1N2_WZ_400p0_200p0_2L2J.png
2ljets_disco_llbb_C1N2N1_GGMHinoZh50_700.png
\end{verbatim}
